`r paste(params$city, params$state, sep = ', ')`

### 2017-11-29 lib/report.Rmd
updating report'
updating
refactoring
updating report
progress

---
params:
  state: "DEFAULT"
  city: "DEFAULT"
  set_title: "DEFAULT"
title: "`r params$set_title`"
---

@@

read_chunk('report.R')
```

```{r part1}
```

```{r part2}
```

>>>>

---
params:
  state: ""
  city: ""
title: "`r paste(params$city, params$state, sep = ', ')`"
---

@@

read_chunk("report.R", labels = "report")
```

```{r report, message=F, warning=F}
```

Total rows: `r total_rows`

```{r by_incident_type_table}
by_incident_type_table
```

```{r by_year_plot}
by_year_plot
```

```{r by_year_by_month_plot}
by_year_by_month_plot
```
